This is the code chunk for reading data
```{r}
activity <- read.csv(file = "activity.csv", header = T, stringsAsFactors = F)
```

What is mean total number of steps taken per day? (Ignore the missing values)
1. Calculate the total number of steps taken per day?

```{r}
activity_1 <- activity[!is.na(activity$steps),]
steps_by_date <- aggregate(steps~date, data=activity_1, FUN = sum)
```

2. Make a histogram of steps taken each day

```{r}
hist(steps_by_date$steps, main = "Histogram of Steps Taken Each Day", 
     xlab = "Steps Taken Per Day", ylab=" Frequency")
```
3. Calculate and report mean and median of the total number of steps taken each day?

```{r}
aggregate <- data.frame(mean=mean(steps_by_date$steps), median=median(steps_by_date$steps))
aggregate
```

  What is the average daily activity pattern
1. Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) 
   and the average number of steps taken, averaged across all days (y-axis)
```{r}
steps_by_interval <- aggregate(steps~interval, data=activity_1, FUN = mean)
plot(steps_by_interval$interval, steps_by_interval$steps, type = "l", xlab="5 minutes interval",
     ylab = "average steps taken across all days")
```

2. Which 5-minute interval, on average across all the days in the dataset, 
   contains the maximum number of steps?
   
```{r}
steps_by_interval[which.max(steps_by_interval$steps),]
```

Imputing Missing Values
1. Calculate and report the total number of missing values in the dataset 
(i.e. the total number of rows with NAs)
```{r}
sum(is.na(activity))
```
2. Devise a strategy for filling in all of the missing values in the dataset. 
   The strategy does not need to be sophisticated. For example, you could use 
   the mean/median for that day, or the mean for that 5-minute interval, etc.
   My strategy is to replace NA values with the mean of the interval
3. Create a new dataset that is equal to the original dataset but with the missing
   data filled in (new activity)
   
```{r}
newactivity <- activity
for(i in 1:17568){
        if(is.na(newactivity$steps[i])){
                newactivity$steps[i] <- steps_by_interval$steps[which(newactivity$interval[i]==steps_by_interval$interval)]
        }
}
```
4. Make a histogram of the total number of steps taken each day and Calculate 
   and report the mean and median total number of steps taken per day. 
   Do these values differ from the estimates from the first part of the
   assignment? What is the impact of imputing missing data on the estimates of 
   the total daily number of steps?
   
```{r}
newstep_by_date <- aggregate(steps~date, data =  newactivity, FUN = sum)
hist(newstep_by_date$steps, col=rgb(0,0,1,1/4), main = "Histogram of Steps Taken Each Day", 
     xlab = "Steps Taken Per Day", ylab=" Frequency")
hist(steps_by_date$steps, col=rgb(1,0,0,1/4), main = "Histogram of Steps Taken Each Day", 
     xlab = "Steps Taken Per Day", ylab=" Frequency", add=T, ylim=c(0,35))
```

Are there differences in activity patterns between weekdays and weekends?
Create a new factor variable in the dataset with two levels - "weekday" and "weekend" indicating whether a given date is a weekday or weekend day.

```{r}
weekdays1 <- c("MOnday", "Tuesday", "Wednesday", "Thursday", "Friday")
newactivity$weekdays <- factor(weekdays(as.Date(newactivity$date))%in%weekdays1, 
                               levels = c(FALSE, TRUE), labels =         
                                       c("weekend","weekday"))
```
Make a panel plot containing a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all weekday days or weekend days (y-axis). See the README file in the GitHub repository to see an example of what this plot should look like using simulated data.
```{r}
newactivity_interval <- aggregate(steps~interval+weekdays, data=newactivity, FUN = mean)
head(newactivity_interval)
library(ggplot2)
qplot(x = interval, y = steps, data = newactivity_interval, facets = weekdays~., geom=c("line"))
?qplot
```


